Research Proposal

### 2024-10-01 assignments/research_proposal/research_proposal.Rmd
update proposal assignment
lecture 9

# Assignment Overview
The goal of this project is to take you through a mock process of publishing in economics, including writing a paper (proposal, in this case) as well as the revise and resubmit process. You will: 1) draft a research proposal, 2) send your proposal to a classmate for peer review, and review one of their proposals, 3) integrate your reviewer's comments into your proposal, and 4) submit the final draft for ``publication'' (i.e. a final grade...).

You **are not** allowed to ``double dip''. This means the idea must be original and you cannot use your second-year paper, or a proposal from another class.

@@

Broadly, you will identify an original and specific research question, explain why it is important, and outline the research design that you will use to address it. After receiving an ``R\&R'' on the paper, you will improve it and submit a final draft at the end of the semester.

## Timeline
\begin{table}[ht]
\begin{tabular}{|c|c|}
\hline
\textbf{Item} & \textbf{Deadline} \\ \hline
First draft     & October 3rd     \\ \hline
Referee report    & October 10th     \\ \hline
Final draft    & October 31st     \\ \hline
\end{tabular}
\end{table}
Note: the first draft is pass/fail. I will check it for completion and award a pass. If you fail to submit a first draft, then five percentage points will be taken off of your final grade.

@@

\clearpage
# Grading Rubric

@@

>>>>

# Assignment Overview
The goal of this project is to take you through a mock process of publishing in economics, including writing a paper (proposal, in this case), the revise and resubmit process, and presenting it. You will: 1) draft a research proposal, 2) send it to a classmate for peer review, and review one of their proposals, 3) integrate your reviewer's comments into your proposal, 4) present your proposal to the class, and 5) submit the final draft for "publication" (i.e. a final grade...) at the end of the semester.

You **are not** allowed to ``double dip''. The idea must be original and you cannot use your second-year paper, or a proposal from another class.

@@

Broadly, you will identify an original research question, explain why it is important, and outline the research design that you will use to address it. After receiving an ``R\&R'', you will improve it and submit a final draft.

## Timeline
\begin{table}[ht]
\begin{tabular}{|c|c|}
\hline
\textbf{Item} & \textbf{Deadline} \\ \hline
First draft     & October 3rd     \\ \hline
Referee report    & October 10th     \\ \hline
Presentations    & October 15/17th     \\ \hline
Final draft    & October 31st     \\ \hline
\end{tabular}
\end{table}
Note: the first draft is pass/fail. I will check it for completion and award a pass. If you fail to submit a first draft, then three percentage points will be taken off of your final grade.

@@

\clearpage
# Grading Rubric: Written Proposal

@@

\clearpage

# Grading Rubric: Proposal Presentation

\begin{table}[h!]
\centering
\begin{tabular}{|p{4cm}|p{8cm}|r|}
\hline
\textbf{Category} & \textbf{Description} & \textbf{Points} \\ \hline
\textbf{Content} &  &  \\ \hline
Introduction \& Research Question & Clear presentation of the research question, its importance, and its relevance to environmental and development economics. & /10 \\ \hline
Theoretical Framework & Presents a coherent theoretical framework. & /15 \\ \hline
Data \& Measurement & Explanation of the data sources, measurements, and units of analysis. Discusses the suitability of data for the research. & /10 \\ \hline
Empirical Strategy & Explains the research design and methodology, including causality and identification strategies. & /15 \\ \hline
\textbf{Delivery} &  &  \\ \hline
Clarity \& Organization & Well-organized presentation, logical flow, and easy to follow. & 10 \\ \hline
Speaking Style \& Engagement & Speaker presents confidently, engages the audience, and maintains good eye contact. & /10 \\ \hline
\textbf{Visual Aids} &  &  \\ \hline
Use of Slides/Visuals & Visual aids are clear, well-designed, and enhance the presentation. & /10 \\ \hline
\textbf{Q\&A Performance} &  &  \\ \hline
Understanding \& Response to Questions & Demonstrates understanding by responding thoughtfully and clearly to questions. Engages respectfully with questions, explaining complex concepts well & /10 \\ \hline
\textbf{Time Management} &  &  \\ \hline
Adheres to Time Limits & Presentation fits within the 20-minute timeframe without rushing. & /10 \\ \hline
\textbf{Total} &  & /100  \\ \hline
\end{tabular}
\end{table}

### 2024-10-01 assignments/research_proposal/research_proposal.tex
update first week
update proposal assignment
lecture 9

@@

The goal of this project is to take you through a mock process of publishing in economics, including writing a paper (proposal, in this case) as well as the revise and resubmit process. You will: 1) draft a research proposal, 2) send your proposal to a classmate for peer review, and review one of their proposals, 3) integrate your reviewer's comments into your proposal, and 4) submit the final draft for ``publication'\,' (i.e.~a final grade\ldots).

You \textbf{are not} allowed to ``double dip'\,'. This means the idea must be original and you cannot use your second-year paper, or a proposal from another class.

@@

Broadly, you will identify an original and specific research question, explain why it is important, and outline the research design that you will use to address it. After receiving an ``R\&R'\,' on the paper, you will improve it and submit a final draft at the end of the semester.

@@

\begin{table}[ht]
\begin{tabular}{|c|c|}
\hline
\textbf{Item} & \textbf{Deadline} \\ \hline
First draft     & October 3rd     \\ \hline
Referee report    & October 10th     \\ \hline
Final draft    & October 31st     \\ \hline
\end{tabular}
\end{table}

@@

\begin{itemize}
\tightlist
\item
  Marc Bellemare's guide on \href{https://marcfbellemare.com/wordpress/wp-content/uploads/2020/09/BellemareHowToPaperSeptember2020.pdf}{how to write applied economics papers}
\item
  Keith Head's \href{https://blogs.ubc.ca/khead/research/research-advice/formula}{introduction formula}
\item
  Plamen Nikolov's \href{https://docs.iza.org/dp15057.pdf}{writing tips for economics research papers}
\item
  Read papers!
\end{itemize}

@@

\hypertarget{grading-rubric}{%
\section{Grading Rubric}\label{grading-rubric}}

@@

>>>>

\textbf{Due date: Final draft due Oct.~31st, 2024}

@@

The goal of this project is to take you through a mock process of publishing in economics, including writing a paper (proposal, in this case), the revise and resubmit process, and presenting it. You will: 1) draft a research proposal, 2) send it to a classmate for peer review, and review one of their proposals, 3) integrate your reviewer's comments into your proposal, 4) present your proposal to the class, and 5) submit the final draft for ``publication'' (i.e.~a final grade\ldots) at the end of the semester.

You \textbf{are not} allowed to ``double dip'\,'. The idea must be original and you cannot use your second-year paper, or a proposal from another class.

@@

Broadly, you will identify an original research question, explain why it is important, and outline the research design that you will use to address it. After receiving an ``R\&R'\,', you will improve it and submit a final draft.

@@

\begin{table}[ht]
\begin{tabular}{|c|c|}
\hline
\textbf{Item} & \textbf{Deadline} \\ \hline
First draft     & October 3rd     \\ \hline
Referee report    & October 10th     \\ \hline
Presentations    & October 15/17th     \\ \hline
Final draft    & October 31st     \\ \hline
\end{tabular}
\end{table}

Note: the first draft is pass/fail. I will check it for completion and award a pass. If you fail to submit a first draft, then three percentage points will be taken off of your final grade.

@@

\begin{itemize}
\tightlist
\item
  Marc Bellemare's guide on \href{https://marcfbellemare.com/wordpress/wp-content/uploads/2020/09/BellemareHowToPaperSeptember2020.pdf}{how to write applied economics papers}
\item
  Keith Head's \href{https://blogs.ubc.ca/khead/research/research-advice/formula}{introduction formula}
\item
  Plamen Nikolov's \href{https://docs.iza.org/dp15057.pdf}{writing tips for economics research papers}
\end{itemize}

@@

\hypertarget{grading-rubric-written-proposal}{%
\section{Grading Rubric: Written Proposal}\label{grading-rubric-written-proposal}}

@@

\hypertarget{grading-rubric-proposal-presentation}{%
\section{Grading Rubric: Proposal Presentation}\label{grading-rubric-proposal-presentation}}

\begin{table}[h!]
\centering
\begin{tabular}{|p{4cm}|p{8cm}|r|}
\hline
\textbf{Category} & \textbf{Description} & \textbf{Points} \\ \hline
\textbf{Content} &  &  \\ \hline
Introduction \& Research Question & Clear presentation of the research question, its importance, and its relevance to environmental and development economics. & /10 \\ \hline
Theoretical Framework & Presents a coherent theoretical framework. & /15 \\ \hline
Data \& Measurement & Explanation of the data sources, measurements, and units of analysis. Discusses the suitability of data for the research. & /10 \\ \hline
Empirical Strategy & Explains the research design and methodology, including causality and identification strategies. & /15 \\ \hline
\textbf{Delivery} &  &  \\ \hline
Clarity \& Organization & Well-organized presentation, logical flow, and easy to follow. & 10 \\ \hline
Speaking Style \& Engagement & Speaker presents confidently, engages the audience, and maintains good eye contact. & /10 \\ \hline
\textbf{Visual Aids} &  &  \\ \hline
Use of Slides/Visuals & Visual aids are clear, well-designed, and enhance the presentation. & /10 \\ \hline
\textbf{Q\&A Performance} &  &  \\ \hline
Understanding \& Response to Questions & Demonstrates understanding by responding thoughtfully and clearly to questions. Engages respectfully with questions, explaining complex concepts well & /10 \\ \hline
\textbf{Time Management} &  &  \\ \hline
Adheres to Time Limits & Presentation fits within the 20-minute timeframe without rushing. & /10 \\ \hline
\textbf{Total} &  & /100  \\ \hline
\end{tabular}
\end{table}
